%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 6CCS3PRJ Final Year Individual Project Report
% luke.day@kcl.ac.uk
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{informatics-report}
\usepackage{color}
\usepackage[square,sort,comma,numbers]{natbib}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{indentfirst}
\usepackage{longtable}
\usepackage{titlesec}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\usepackage{float}
%\floatstyle{boxed}
%\restylefloat{figure}
\lstset{frame=single,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}



 %References
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Front Matter - project title, name, supervisor name and date
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{6CCS3PRJ\\\vspace{0.2cm}Dining Cryptographers Network Simulation Tool}
\author{Federico Capaldo}
\studentID{1444686}
\supervisor{Professor Luca Viganó}

\date{\today}

\abstractFile{FrontMatter/abstract.tex}
\ackFile{FrontMatter/acknowledgements.tex} %Remove line if you do not want acknowledgements


\titleformat{\subparagraph}
    {\normalfont\normalsize\bfseries}{\thesubparagraph}{1em}{}
\titlespacing*{\subparagraph}{\parindent}{3.25ex plus 1ex minus .2ex}{.75ex plus .1ex}

\begin{document}
\setcounter{secnumdepth}{5}

\createFrontMatter
\onehalfspacing
\tableofcontents
\doublespacing



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Report Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can write each chapter directly here or in a separate .tex file and use the include command.

\include{Chapters/Intoduction}
\include{Chapters/Background}
\include{Chapters/ReqSpec}
\include{Chapters/Design}
\include{Chapters/Implementation}
\include{Chapters/ProfessionalIssues}
\include{Chapters/Evaluation}
\include{Chapters/Conclusion}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plain}
\bibliography{references}
\addcontentsline{toc}{section}{Bibliography}
\begin{thebibliography}{99}

\bibitem{Chaum} Chaum, D. (1988). The dining cryptographers problem: Unconditional sender and recipient untraceability. Journal of Cryptology, [online] 1(1). Available at: http://www.cs.ucsb.edu/~ravenben/classes/595n-s07/papers/dcnet-jcrypt88.pdf [Accessed 10 Mar. 2017].

\bibitem{Anonymity} Oxford Dictionary of English, "Anonymity", 2017

\bibitem{Malkhi} D. Malkhi, "Advanced Course in Computer and Network Security", Jerusalem 2002 - http://www.cs.huji.ac.il/~ns/Anonymity.pdf

\bibitem{Pfitzmann} A. Pfitzmann, M. Kohntop,"Anonymity, Unobservability, and Pseudonymity – A Proposal for Terminology", Germany 2001

\bibitem{Franck} C. Franck, "New Directions for Dining Cryptographers", Luxembourg 2008 - https://secan-lab.uni.lu/images/stories/christian{\_}franck/FRANCK{\_}Christian{\_}Master{\_}Thesis.pdf

\bibitem{Diffie1} W. Diffie, M. E. Hellman, "New Directions in Cryptography", 1976 https://ee.stanford.edu/~hellman/publications/24.pdf

\bibitem{Fischer} Fischer-Hubner, S. (2001). IT-security and privacy. Berlin: Springer, pp.125-128.

\bibitem{Lewin} M. Lewin, "ACCU - All About XOR", 2012 https://accu.org/index.php/journals/1915

\bibitem{Scholz} I. Scholz, "Dining Cryptographers - The Protocol", http://www.eigenheimstrasse.de/svn/dc

\bibitem{wiki1} Wikipedia, "Secure multi-party computation". https://en.wikipedia.org/wiki/Secure{\_}multi-party{\_}computation

\bibitem{Golle} P. Golle, A. Juel, "Dining Cryptographers Revisited", 2004, https://www.freehaven.net/anonbib/cache/golle:eurocrypt2004.pdf 


\end{thebibliography}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appendices
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\include{Appendices/UserGuide}
\include{Appendices/Examples}

\end{document}
